---
title: "Homework_one"
author: "Brooke Wheeler"
date: "1/14/2022"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(lubridate)
library(dplyr)
```


# 1 Use and show R coding to find the number of days from June 6th 2020 to July 14th 2021

```{r}
two_yearago <- ymd(20200606)

last_year <- ymd(20210714)

two_yearago - last_year


```

# 2 Use and show R coding to confirm that the year 1988 was a leap year.
```{r}
year_1988 <- ymd(19880101)
year_1989 <- ymd(19890101)
year_1988 - year_1989

# the year 1988 was a leap year since it had 366 days rather than 365
```

# 3 Use and show R coding to confirm that the year 1989 was not a leap year
```{r}
year_1990 <- ymd(19900101)
year_1989 <- ymd(19890101)
year_1990 - year_1989

# the year 1989 was not a leap year since it had 365 days rather than 365
```

# 4 Why is there months() but no dmonths ? (Answer in 3 to four sentences)

## Using durations such as dhours or dminutes or ddays gives you the exact number in seconds. You can't use dmonths since each month does that have the same amount of days so theres not a standard that can be multiplied to find the exact number of seconds. When using months() you are just saying the amount of months or which month. 

# 5 John was born April 11th, 1962. Use and show R coding to determine how old John is in years
```{r}
birthday <- ymd(19620411)
(today() %--% birthday)%/% years(1)

# he is 59 years old

```

# 6 Modify the flights_dt coding in the notes or the book to obtain the following partial data table shown below.  Show all required coding. (Most of the coding needed is provided in the notes)
```{r}
library(nycflights13)

make_datetime_100 <- function(year, month, day, time) {
  make_datetime(year, month, day, time %/% 100, time %% 100)
}

flights %>% 
  filter(!is.na(dep_time), !is.na(arr_time)) %>% 
  mutate(
    dep_time = make_datetime_100(year, month, day, dep_time),
    arr_time = make_datetime_100(year, month, day, arr_time),
    sched_dep_time = make_datetime_100(year, month, day, sched_dep_time),
    sched_arr_time = make_datetime_100(year, month, day, sched_arr_time)
  )  ->

flights_dt
flights_dt

flights_dt %>%
  select(origin, dest, carrier, arr_time, dep_time) -> new_flights
new_flights
```

# 7  Now, using your table from #6, produce the frequency plot shown which conveys frequency counts for the months of April, July, and October for the year 2013
```{r}
new_flights %>%
  filter(dep_time >= ymd(20130401) & dep_time <= ymd(20131030)) %>%
  ggplot(aes(dep_time))+
  geom_freqpoly(binwidth = 86400)

```
# 8 Now use dplyr functions to produce a data table that shows arrival times for American Airlines at the Dallas Fort Worth Airport from the LaGuardia airport in New York. Your output should show rows 115 to 125.
```{r}
new_flights %>%
  select(origin, dest, carrier, arr_time) %>%
  filter(origin == "LGA",
         dest == "DFW",
         carrier == "AA") %>%
  slice(115:125)
```

# 9 Using the first two observational date time designations from your #8 table, Use and show R code to confirm that there are 181 minutes time intervals between them.
```{r}
row115 <- ymd_hms("2013-01-09 16:16:00")
row116 <- ymd_hms("2013-01-09 19:17:00")
(row116 -row115) / dminutes(1)
```






